Making Sequential Programs Deterministic

### 2019-03-31 design.tex

\TheDeterminismChecker has additional type refinement rules for the sorting
methods such as \<List.sort>, \<Collections.sort>, and \<Arrays.sort>:
 as shown in \cref{fig-sorting}.
\begin{figure}
%     $\infer[\rulename{list sort}]{\Gamma \vdash x : \|Det \ List|\angles{\|Det| \ \beta}}{\Gamma \vdash x : \|OrderNonDet \ List|\angles{\|Det| \ \beta} & \|x.sort()|}$
%     
%     \bigskip

>>>>

\TheDeterminismChecker has additional type refinement rules for the sorting
methods of \<List>, \<Collections>, and \<Arrays> classes
 as shown in \cref{fig-sorting}.
\begin{figure}
%     $\infer[\rulename{list sort}]{\Gamma \vdash x : \|Det \ List|\angles{\|Det| \ \beta}}{\Gamma \vdash x : \|OrderNonDet \ List|\angles{\|Det| \ \beta} & \|x.sort()|}$
%     
%     \bigskip

### 2019-03-31 experiments.tex

\section{Evaluation}
\begin{itemize}
    \item goals of evaluation: Compare with NonDex and Deflaker
    \item Quantitative comparison: \TheDeterminismChecker finds all bugs reported by NonDex and Deflaker?
    \item Qualitative study of the issues discovered.
    \item System info: 2.3 GHz Intel Core i5, 8 GB 2133 MHz
\end{itemize}

\subsection{Running NONDEX on Randoop}
To evaluate how existing tools perform on large programs, we ran the tool \href{https://github.com/TestingResearchIllinois/NonDex}{NONDEX~\cite{nondex}} on 
\href{https://github.com/randoop/randoop}{Randoop~\cite{randoop}}.
We followed the instructions to build the project with the gradle plugin. 
NONDEX terminated without reporting any flaky tests.
\todo{check if the bugs discovered by \TheDeterminismChecker have test coverage}
\todo{We investigated the tests covering code that \TheDeterminismChecker reported as nondeterministic.
If code is covered by tests, NONDEX couldn't discover it. Else, its a limitation of NONDEX}.
This indicates that the additional programmer effort required by \TheDeterminismChecker is justified
as our tool discovers non-trivial issues and doesn't depend on code coverage or other runtime heuristics.

>>>>

\section{Comparison to previous work}

The state of the art in flaky test detection is NonDex~\cite{nondex}.
\Cref{sec:related} explains how NonDex works.

\begin{itemize}
    \item goals of evaluation: Compare with NonDex and Deflaker
    \item Quantitative comparison: \TheDeterminismChecker finds all bugs reported by NonDex and Deflaker?
    \item Qualitative study of the issues discovered.
    \item System info: 2.3 GHz Intel Core i5, 8 GB 2133 MHz
\end{itemize}

\subsection{Case study with NonDex}\label{sec:nondex-randoop}

We ran NonDex on the same commit of Randoop as we used for the case study
of \cref{sec:case-study}.  This version contains 3 nondeterminism bugs that
\ourTool found.

We modified Randoop by deleting tests that were skipped by its buildfile,
because the NonDex gradle plugin does not respect those settings.

After that, NonDex ran without problems on Randoop.
It completed successfully without reporting any flaky tests.

\todo{check if the bugs discovered by \theDeterminismChecker have test coverage}
\todo{We investigated the tests covering code that \theDeterminismChecker reported as nondeterministic.
If code is covered by tests, NONDEX couldn't discover it. Else, its a limitation of NONDEX}.
This indicates that the additional programmer effort required by \TheDeterminismChecker is justified
as our tool discovers non-trivial issues and doesn't depend on code coverage or other runtime heuristics.
